paper2_resistance_mechanisms_mixtures

### 2016-05-20 inst/documents/keep_old_insecticide.Rmd
moved documents into own folder

---
  title: "paper1_results_figs"
  output: pdf_document
  author: "Andy South"
  date: "`r Sys.Date()`"
---

# Figures for paper 1 
# version 5 - in progress

## Based on 10000 runs with all inputs varying at once which explains the variability at particular input values.

Comparing these insecticide use strategies:

1. Single use
1. Mixture (either AI) : threshold reached for either insecticide
1. Adaptive mixture : threshold reached for either insecticide, switch to sole use of other until it too reaches threshold
1. Mixture (both AIs) : threshold reached for both insecticides in mixture
1. Sequential : sole use of one insecticide, switch to other when threshold reached until it too reaches threshold

Renamed from previous naming system :
Mixture (either AI)   [mixture1]
Mixture (both AIs)    [mixture3]
Adaptive mixture      [mixture2]

## Notable results

1. Time-to-resistance is lowest for single use and for the first insecticide in a mixture. Time-to-resistance is highest for the 2nd insecticide in a mixture.
1. In between these extremes, there is less difference between the alternative strategies of a) sequential and b) adaptive mixture switching to sole use. The latter takes slightly longer to reach the threshold.
1. Exposure and effectiveness seem to be the most important inputs.
1. Exposure has the greatest effect on time-to-resistance.
1. Effectiveness of the insecticides is the one input that has a notably different effect on the strategies of a) sequential and b) adaptive mixture switching to sole use. Below an effectiveness of ~0.55 to 0.6 sequential takes longer, and above this 'mixture switching to sole use' takes longer.

@@

  library(resistance)

@@

  dif_oldnew_newonly["mix_minus_sole0.5"] <- dif_oldnew_newonly["gen_cP0.5"] - dif_oldnew_newonly["gen_cP0.5seq"]

@@

  #not sure I need to do this because all results already show mixture better
  #now I want to subset just those runs where start freq old is > 10 * new

@@

  #28/4/16 testing Ians statement
  #does resistance always arise faster in sole use than in a mixture (irrespective of starting frequencies)
  #resistPointsI1_T #"insecticide 1" 
  #resistPointsI2_T #"insecticide 2"
  #resistPointsMixI1_T #"I1inMix" 
  #resistPointsMixI2_T #"I2inMix"

  mix_minus_soleI1 <- resistPointsMixI1_T["gen_cP0.5"] - resistPointsI1_T["gen_cP0.5"]
  which( mix_minus_soleI1 < 0 ) 
  #0
  mix_minus_soleI2 <- resistPointsMixI2_T["gen_cP0.5"] - resistPointsI2_T["gen_cP0.5"]
  which( mix_minus_soleI2 < 0 ) 
  #0

  #so yes in our param space adding an extra insecticide always increases resistance time for the first

  #i could plot it against exposure & effectiveness

@@

---

# Fig. x1 Time-to-resistance across all input values

```{r, eval=TRUE, echo=FALSE, warning=FALSE}

  library(ggplot2)

#names_results <- c("time_to_resistance0.5","time_to_resistance0.25","time_to_resistance0.1")
names_results <- c("time_to_resistance0.25")

ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 2"), ]

for(i in names_results)
{
  #x11()

  print( ggplot(ggSubset, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      coord_cartesian( ylim=c(0, 350)) +
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) +
      #scale_x_discrete("Resistance to which insecticide", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Sole use", "Mix either"="1st in mix","Sequential"="2nd in sequence", "Mix adaptive"="2nd in mix\nswitch to sole", "Mix both"="2nd in mix" ) )
      scale_x_discrete("Resistance to which insecticide", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Sole use", "Mix either"="1st in mix","Sequential"="2nd in sequence", "Mix adaptive"="adaptive mix", "Mix both"="2nd in mix" ) )

  ) #end print
}

## Fig. x2 How time-to-resistance is effected by input values for each insecticide use strategy

  names_inputs <- names(ggInsOuts)[1:num_inputs]

  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]

    y <- 'time_to_resistance0.25'

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #tryting to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

           )
  }

## Fig. x3 How difference in time-to-resistance between sequential and adaptive mixture is effected by input values

  ggSubset <- dif_mixA_seq

    y <- "mixA_minus_seq0.25"

    print( ggplot(ggSubset, aes_string(x=i, y=y)) + #, colour="strategy")) + 
            #points not wanted if 10000
             geom_point(shape=1, colour="darkblue", alpha=0.2, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1, colour="red") +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i) +
             geom_hline(yintercept = 0, colour="white")
           )
  }

@@

@@

    x <- dif_oldnew_newonly[,1:num_inputs]
    y <- dif_oldnew_newonly["mix_minus_sole0.5"]

@@

    #if you add bootstrap, error bars are added to the default plot & extra columns to the PRCC object
    #pcc_res <- pcc(x, y, rank=TRUE, nboot=100)
    #plot(pcc_res)

    #results are here I can probably rbind them together into a df that I can ggplot
    #pcc_res$PRCC

@@

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste("PRCC benefit of mix old+new over sole new (old=1, new=2)")) +
             xlab(NULL)
          )
```

  #can I do a 2D hexbin plot with x=exposure, y=effectiveness
  #but do I just want to use 1 effectiveness, or maybe add both effectivenesses together ?
  #bin colour : proportion of runs in which sequential better & could have diverging scale about 0.5
  #I probably still need to tweak data first
  #currently I have differences in times to resistance : mixA_minus_seq0.25
  #what I think I want is the proportion of runs in which mix is better
  #I can get that by setting to 0 & 1 and calc average
  # tst_runs <- c(1,0,0,0)
  # tst_runs <- c(1,1,1,0)
  # mean(tst_runs)

  ##BEWARE toogle this to look at plots for mixboth vs seq
  ggSubset <- dif_mixA_seq
  #ggSubset <- dif_mix2_seq

  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mixA_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 > 0, 1, 0 )
  ggSubset$seq_better_mixA0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 < 0, 1, 0 )
  ggSubset$abs_mixA_minus_seq0.25 <- abs(ggSubset$mixA_minus_seq0.25)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$mixA_minus_seq0.25==0),]
  #set these to 1 (they were 0)
  df_same$mixA_better_seq0.25 <- 1
  df_same$seq_better_mixA0.25 <- 1
  #rbind them back onto other dataset, probably not needed ??
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mixA_not20pc_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 / ggSubset$gen_cP0.25seq <= 0.2, 1, 0 )

    #failed hex plot just gave me counts
    # print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.25'))+
    #          geom_hex()
    #        )

    #interesting plot showing where sequence is better is restricted to higher values of exposure and effectiveness 
    print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.25'))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #can I multiply the two effectivenesses together ?
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_better_seq0.25))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mixA_better_seq0.25))+

             geom_point(alpha=0.2)  
           )

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mixA0.25))+
             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

             theme(legend.position="none") +
             geom_point(alpha=1)  
           )

    #what if I do the difference rather than just 0/1
    #aha! this is close to being the killer plot, just need to get the colour scale right 
    #but the previous one may be clearer
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_minus_seq0.25))+
             #geom_hex()
             geom_point(alpha=1) +
             #no adding grey outlines obscures the pattern
             #geom_point(shape=21, colour='grey') +
             #this one does look good but slight potential to see negatives above even though they aren't there
             #could I modify the shapes to be different
             #would a repeated, faceted plot solve that ?
             #scale looks good but colours could do with being denser
             #and I'm not sure that making the points that are close to zero white is a good idea ?
             #although it does mean points that are only a few generations different do not obscure the pattern
             #maybe I could explicitly do Ians 20% thing & colour those white
             scale_colour_gradient2()

             #didn't manage to get the colorBrewer scale to diverge from 0
             #scale_colour_distiller("RdYlGn",type='div')
            )

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25))+

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

    #NOW what if I subset the 0 values & fit a linear model to it
    #could that be used to decide between the 2 strategies ?
    #I might even be able to do the lm plot within ggplot

    #trickiness I have is that I have previously put 0 values in the adptive mix better plot 
    #which is maybe a little misleading anyway
    #and also means that I only get the lm line in the one plot
    #maybe what I can do is add the zeros into both plots then  will get lines in both
    #might even be good to overplot the zero values after
    #or even remove the zero values ?

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25))+

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points mixA_minus_seq0.25
             geom_smooth(data=ggSubset[which(ggSubset$mixA_minus_seq0.25==0),], method = "lm", se = FALSE) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$mixA_minus_seq0.25==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +            
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  # doing the lm outside of ggplot    
  df_same = ggSubset[which(ggSubset$mixA_minus_seq0.25==0),]
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

  l_mod <- lm(y1 ~ x1)
  l_mod$coefficients
  #(Intercept)           x 
  #  0.9790948   0.6095132

  x2 <- seq(0,1,0.1)
  #approximation
  y2 <- 0.6*x2+0.98
  #plot(x2,y2)

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_mixA_minus_seq0.25))+

             facet_grid( ~ mixA_not20pc_better_seq0.25, labeller=as_labeller( c('0'='adaptive mix\nresistance >20% slower','1'='adaptive mix\nresistance <20% slower'))) +

             theme_bw() +
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points
             geom_smooth(data=df_same, method = "lm", se = FALSE) 
           )

@@

# repeating killer plot for mixtures both versus sequential
```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

  #try repeating the killer plot for mixtures both versus sequential

  ##BEWARE toogle this to look at plots for mixboth vs seq
  #ggSubset <- dif_mixA_seq
  ggSubset <- dif_mix2_seq

  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mix2_better_seq0.25 <- ifelse( ggSubset$mix2_minus_seq0.25 > 0, 1, 0 )
  ggSubset$seq_better_mix20.25 <- ifelse( ggSubset$mix2_minus_seq0.25 < 0, 1, 0 )
  ggSubset$abs_mix2_minus_seq0.25 <- abs(ggSubset$mix2_minus_seq0.25)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$mix2_minus_seq0.25==0),]
  #set these to 1 (they were 0)
  df_same$mix2_better_seq0.25 <- 1
  df_same$seq_better_mix20.25 <- 1
  #rbind them back onto other dataset, probably not needed ??
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mix2_not20pc_better_seq0.25 <- ifelse( ggSubset$mix2_minus_seq0.25 / ggSubset$gen_cP0.25seq <= 0.2, 1, 0 )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mix2_better_seq0.25))+

             geom_point(alpha=0.2)  
           )

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mix20.25))+
             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +

             theme(legend.position="none") +
             geom_point(alpha=1)  
           )

    #killer plot mix2 vs seq
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.25))+

             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +

             #YlGnBu looks really good except that the yellow points are very faint
             #scale_colour_distiller(palette='YlGnBu', direction=1) +
             #option="plasma" looks good too
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #theme_minimal() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             #failing to add legend for curtis point
             #scale_fill_manual(name = "Curtis Fig.2", values = 'red', labels = 'test') +
             #scale_size_manual(name = "Curtis Fig.2", values="test") +
             #scale_shape_manual(name = "Curtis Fig.2", values="test") +             
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.25))+

             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_mixA_minus_seq0.25))+

             facet_grid( ~ mix2_not20pc_better_seq0.25, labeller=as_labeller( c('0'='mix\nresistance >20% slower','1'='mix\nresistance <20% slower'))) +

             theme_bw() +
             #add point for Curtis inputs
             #geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) +
             #add a lm fitted to the 0 points
             geom_smooth(data=df_same, method = "lm", se = FALSE) 
           )

# Some examples showing how changing effectiveness can alter the ranking of insecticide strategies
### Curtis' Fig 2. inputs : mix2 > adaptive > mix1 > seq
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### decrease effectiveness of I2 from 1 to 0.85 : mix2 > adaptive > seq > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### also decrease effectiveness of I1 from 0.73 to 0.63 : seq > mix2 > adaptive > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.63 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

# PRCC difference in time-to-resistance between sequential and mixture adaptive
```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

    x <- dif_mixA_seq[,1:num_inputs]
    y <- dif_mixA_seq["mixA_minus_seq0.25"]

    #if you add bootstrap, error bars are added to the default plot & extra columns to the PRCC object
    #pcc_res <- pcc(x, y, rank=TRUE, nboot=100)
    #plot(pcc_res)

    #results are here I can probably rbind them together into a df that I can ggplot
    #pcc_res$PRCC

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             ggtitle(paste("PRCC difference between sequential and mixture adaptive")) +
             xlab(NULL)
          )
```

# PRCC analysis for time-to-resistance subsetted by each insecticide use strategy
```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

# pcc(X, y, rank = FALSE, nboot = 0, conf = 0.95)
# 
# Arguments
# X a data frame containing model input variables
# y a vector containing the responses 
# rank logical. If TRUE, the analysis is done on the ranks.
# nboot the number of bootstrap replicates.
# conf the confidence level of the bootstrap confidence intervals.

  strategies <- unique(ggInsOuts$strategy)

  for(strategy in strategies)
  {

    by_strategy <- ggInsOuts[ggInsOuts$strategy==strategy,]

    x <- by_strategy[,1:num_inputs]
    y <- by_strategy['time_to_resistance0.25']

    #if you add bootstrap, error bars are added to the default plot & extra columns to the PRCC object
    #pcc_res <- pcc(x, y, rank=TRUE, nboot=100)
    #plot(pcc_res)

    #results are here I can probably rbind them together into a df that I can ggplot
    #pcc_res$PRCC

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             #ggtitle(paste(strategy,"PRCC")) +
             ggtitle(paste(strategy,"time-to-resistance 0.25")) +
             xlab(NULL)
          )
  }

## response of resistance thresholds to individual inputs faceted by strategy
```{r, eval=TRUE, echo=FALSE, fig.height=3.5}

  names_inputs <- names(ggInsOuts)[1:num_inputs]

  #todo find out to take sample this doesn't work
  #ggSample <- sample(ggInsOuts,500)

    y <- 'time_to_resistance0.25'    
    #y <- 'time_to_resistance0.5'
    color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    #color <- 'exposure'

    print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
             #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             geom_smooth(colour='red', linetype='dashed',size=0.5, show.legend=FALSE) +
             facet_wrap( ~ strategy) + #, show_guide = FALSE) + 
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i))
  }

>>>>

---
  title: "keep on an old insecticide in a mix ?"
  output: pdf_document
  author: "Andy South"
  date: "`r Sys.Date()`"
---

## new analysis April 2016 for paper1 : v2

Is keeping on an old insecticide in a mix better than just using a new insecticide on its own ?

Short answer : Yes

(part copied from paper1_results_figs.Rmd)

This analysis uses previous sensitivity analysis runs :
1. select out runs where the starting frequency of resistance to I1 > I2
1. I didn't yet restrict to runs where there was a 10 fold difference in starting frequencies, seemed not to be necessary.

# Notable results
1. it is always better to keep on the old insecticide rather than using the new insecticide on its own.
1. exposure (to both insecticides) and effectiveness of the old insecticide have the main effect on how much better the mixture is over sole use. Exposure has a positive effect, and effectiveness a negative effect on the benefit of the mixture.
1. dominance and selection coefficient for the new insecticide have a lesser effect (also negative) on the benefit of the mixture

@@

library(resistance)
library(ggplot2)

@@

dif_oldnew_newonly["mix_minus_sole0.5"] <- dif_oldnew_newonly["gen_cP0.5"] - dif_oldnew_newonly["gen_cP0.5seq"]
# %add_div
dif_oldnew_newonly["mix_divby_sole0.5"] <- dif_oldnew_newonly["gen_cP0.5"] / dif_oldnew_newonly["gen_cP0.5seq"]

@@

#****************
#not sure I need to do this because all results already show mixture better
#now I want to subset just those runs where start freq old is > 10 * new

@@

@@

\pagebreak

## Fig. xx1 Recreating analysis from Curtis Table 1 (vi)

```{r, eval=TRUE, echo=FALSE, fig.height=4.5}

runcurtis_f2( P_1 = 0.001,
P_2 = 0.01,
# dominances
h.RS1_A0 =  1,
h.RS2_0B =  1,
# exposures
exposure =  0.9,
# effectivenesses
phi.SS1_A0 =  1,
phi.SS2_0B =  1,
# selection coefficients
s.RR1_A0 =  1,
s.RR2_0B =  1,
addCombinedStrategy=FALSE,
addStrategyLabels = FALSE )
```

This seems to show that resistance to the new insecticide (red) rises faster when alone (dotted) than when in combination (solid) with an old insecticide at a higher frequency. This is contrary to what Curtis said.

Also note that resistance arises much faster than in our sensitivity runs. I think  this is because the selection coefficients (1) are much higher than the range we use (0.1-0.45).

\pagebreak

@@

#mix_divby_sole0.5
for(i in names_inputs)
{
  #x11()

  y <- "mix_divby_sole0.5"

@@

x <- dif_oldnew_newonly[,1:num_inputs]

y <- dif_oldnew_newonly["mix_minus_sole0.5"]

@@

@@

print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
         geom_point(shape=1, colour='red') +
         theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
         geom_hline(yintercept = 0, linetype=3) +
         ylim(-1,1) +
         ggtitle(paste("Difference time-to-resistance for mix old+new minus new alone (old=1, new=2)")) +
         xlab(NULL)
)

#mix_divby_sole0.5
y <- dif_oldnew_newonly["mix_divby_sole0.5"]

print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
         geom_point(shape=1, colour='red') +
         theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
         geom_hline(yintercept = 0, linetype=3) +
         ylim(-1,1) +
         ggtitle(paste("Ratio of time-to-resistance for mix old+new over new alone (old=1, new=2)")) +
         xlab(NULL)
)

@@
